Case study: Genome-Wide Association Analyses (GWAS)

### 2018-05-25 datasets/GWAS/GWAS.Rmd
Add method heatmaps to case studies with more than one covariate/comparison
Save effect size in bench object

```{r, GWAS1-sb, results="hide", message=FALSE}
duration <- NA
if (!file.exists(resfile_N)) {
    t1 <- proc.time()
    sbN <- bd %>% buildBench(data=(bmi %>% mutate(ind_covariate=ind_covar_N)), 
                             ftCols = c("ind_covar_N"),
                             parallel=TRUE, BPPARAM=multicoreParam)
    metadata(sbN)$data_download_link <- 
                    "http://portals.broadinstitute.org/collaboration/giant/images/3/3a/BMI.SNPadjSMK.zip"
    saveRDS(sbN, file = resfile_N)
    duration <- round((proc.time()-t1)[3]/60,1)
} else {
    sbN <- readRDS(resfile_N)
}
```

@@

```{r, GWAS1-sb2, results="hide", message=FALSE}
duration <- NA
if (!file.exists(resfile_AF)) {
    t1 <- proc.time()
    sbAF <- bd %>% buildBench(data=(bmi %>% mutate(ind_covariate=ind_covar_AF) %>%
                                    filter(!is.na(ind_covariate))), 
                              ftCols = c("ind_covar_AF"),
                              parallel=TRUE, BPPARAM=multicoreParam)
    metadata(sbAF)$data_download_link <-    
                     "http://portals.broadinstitute.org/collaboration/giant/images/3/3a/BMI.SNPadjSMK.zip"
    saveRDS(sbAF, file = resfile_AF)
    duration <- round((proc.time()-t1)[3]/60, 1)
} else {
    sbAF <- readRDS(resfile_AF)
}
```

@@

```{r, fig.width=8, fig.height=3.5}
mcols(sbN)$effect_size <- bmi %>% filter(!is.na(ind_covar_N)) %>% pull(effect_size)
covariateLinePlot(sbN, alpha=0.05, covname="effect_size", nbins=25, 
                 trans="log1p")
covariateLinePlot(sbN, alpha=0.05, covname="ind_covar_N", nbins=25, 
                 trans="log1p")
```

@@

```{r, fig.width=8, fig.height=3.5}
mcols(sbAF)$effect_size <- bmi %>% filter(!is.na(ind_covar_AF)) %>% pull(effect_size)
covariateLinePlot(sbAF, alpha=0.05, covname="effect_size", nbins=25, 
                 trans = "log1p")
covariateLinePlot(sbAF, alpha=0.05, covname="ind_covar_AF", nbins=25)
```

>>>>

```{r, GWAS1-sb, results="hide", message=FALSE}
duration <- NA
if (!file.exists(resfile_N)) {
    t1 <- proc.time()
    sbN <- bd %>% buildBench(data=(bmi %>% mutate(ind_covariate=ind_covar_N)), 
                             ftCols = c("ind_covar_N", "effect_size"),
                             parallel=TRUE, BPPARAM=multicoreParam)
    metadata(sbN)$data_download_link <- 
                    "http://portals.broadinstitute.org/collaboration/giant/images/3/3a/BMI.SNPadjSMK.zip"
    saveRDS(sbN, file = resfile_N)
    duration <- round((proc.time()-t1)[3]/60,1)
} else {
    sbN <- readRDS(resfile_N)
}
```

@@

```{r, GWAS1-sb2, results="hide", message=FALSE}
duration <- NA
if (!file.exists(resfile_AF)) {
    t1 <- proc.time()
    sbAF <- bd %>% buildBench(data=(bmi %>% mutate(ind_covariate=ind_covar_AF) %>%
                                    filter(!is.na(ind_covariate))), 
                              ftCols = c("ind_covar_AF", "effect_size"),
                              parallel=TRUE, BPPARAM=multicoreParam)
    metadata(sbAF)$data_download_link <-    
                     "http://portals.broadinstitute.org/collaboration/giant/images/3/3a/BMI.SNPadjSMK.zip"
    saveRDS(sbAF, file = resfile_AF)
    duration <- round((proc.time()-t1)[3]/60, 1)
} else {
    sbAF <- readRDS(resfile_AF)
}
```

@@

```{r, fig.width=8, fig.height=3.5}
covariateLinePlot(sbN, alpha=0.05, covname="effect_size", nbins=25, 
                 trans="log1p")
covariateLinePlot(sbN, alpha=0.05, covname="ind_covar_N", nbins=25, 
                 trans="log1p")
```

@@

```{r, fig.width=8, fig.height=3.5}
covariateLinePlot(sbAF, alpha=0.05, covname="effect_size", nbins=25, 
                 trans = "log1p")
covariateLinePlot(sbAF, alpha=0.05, covname="ind_covar_AF", nbins=25)
```

# Covariate comparison

Here we compare the method ranks for the two covariates at alpha = 0.10.

```{r}
plotMethodRanks(c(resfile_AF, resfile_N), 
                colLabels = c("MAF", "Sample Size"), 
                alpha = 0.10, xlab = "Covariate", 
                excludeMethods = NULL)
```
